A Fast and Tight Heuristic for A* in Road Networks

### 2021-09-28 paper/ch_potentials.tex
math formatting
switch to acm template for jea

\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}

\usepackage{amssymb}
\usepackage{amsmath}
% checkmarks
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[algo2e,vlined]{algorithm2e}

@@

\nolinenumbers
\hideLIPIcs

@@

\title{A Fast and Tight Heuristic for A* in Road Networks}
\author{Ben Strasser}{Germany}{academia@ben-strasser.net}{}{}
\author{Tim Zeitz}{Karlsruhe Institute of Technology, Germany}{tim.zeitz@kit.edu}{https://orcid.org/0000-0003-4746-3582}{}

\authorrunning{B. Strasser and T. Zeitz}
\Copyright{Ben Strasser and Tim Zeitz}

@@

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{David Coudert and Emanuele Natale}
\EventNoEds{2}
\EventLongTitle{19th International Symposium on Experimental Algorithms (SEA 2021)}
\EventShortTitle{SEA 2021}
\EventAcronym{SEA}
\EventYear{2021}
\EventDate{June 7--9, 2021}
\EventLocation{Nice, France}
\EventLogo{}
\SeriesVolume{190}
\ArticleNo{6}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For sake of keeping this section self-contained, we now briefly reiterate the details of our configuration.
The stretch limited to $\epsilon = 0.25$, i.e. for any path $P = (u,\dots,v)$ in the alternative graph $w(P) \leq (1+\epsilon) \dist(u,v)$.
Shortest path edges are penalized multiplicative with a factor of $\psi = 1.1$, i.e. when an edges was $k$ times on a shortest path its weight will be $w_q = w_{\ell}\cdot\psi^k$.
We also penalize edges incident to shortest paths with an asymmetric additive rejoin penalty.
An edge $uv$ where $u$ is on a shortest path but $v$ is not will get its weight increased by $\psi_r \cdot \dist_{w_{\ell}}(s,t) \cdot \frac{\dist_{w_q}(s,u)}{\dist_{w_q}(s,t)}$.
An edge $uv$ where $v$ is on a shortest path but $u$ is not will get its weight increased by $\psi_r \cdot \dist_{w_{\ell}}(s,t) \cdot \frac{\dist_{w_q}(v,t)}{\dist_{w_q}(s,t)}$.
$\psi_r$ is set to 0.01.
To avoid over-penalization, we count the times a \emph{node} was on a shortest path and do not apply penalties, when this number exceeds $k_{\max} := \lceil\log_{\psi}(1+\epsilon)\rceil + 2$.
Shortest paths are split into segments not yet contained in the alternative graph.
A segment is only added if it is long enough (at least $0.05 \cdot \dist_{w_{\ell}}(s,t)$) and does not violate the maximum stretch condition.
We terminate the algorithm when any of the following conditions becomes true:
\begin{itemize}
	\item All nodes on the current shortest path have been penalized $k_{\max}$ times.
	\item 10 ore more segments have been added to the alternative graph.
	\item The shortest path is longer than $(1+\epsilon) \cdot \dist_{w_{\ell}}(s,t)$ with respect to the original metric.
	\item The shortest path is longer than $(1+\epsilon) \cdot \psi + 2\psi_r \cdot \dist_{w_{\ell}}(s,t)$ with respect to the penalized metric.
\end{itemize}
The last two stopping criteria can both be utilized for additional pruning in the A*.
As a final optimization, we run the forward and backward search in parallel in two threads.

>>>>

% \documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
\documentclass[manuscript,review]{acmart}

% \usepackage{amssymb}
% \usepackage{amsmath}
% checkmarks
\usepackage{pifont} % TODO
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

\usepackage{todonotes}
% \usepackage{booktabs}
\usepackage{multirow}
\usepackage[algo2e,vlined]{algorithm2e}

@@

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

@@

\title{A Fast and Tight Heuristic for A* in Road Networks}

\author{Ben Strasser}
\email{academia@ben-strasser.net}
\affiliation{}

\author{Tim Zeitz}
\email{tim.zeitz@kit.edu}
\orcid{0000-0003-4746-3582}
\affiliation{%
  \institution{Institute of Theoretical Informatics, Algorithmics I, Karlsruhe Institute of Technology}
  \city{Karlsruhe}
  \country{Germany}
}

% \author{Ben Strasser}{Germany}{academia@ben-strasser.net}{}{}
% \author{Tim Zeitz}{Karlsruhe Institute of Technology, Germany}{tim.zeitz@kit.edu}{https://orcid.org/0000-0003-4746-3582}{}

% \authorrunning{B. Strasser and T. Zeitz}
\renewcommand{\shortauthors}{B. Strasser and T. Zeitz}
% \Copyright{Ben Strasser and Tim Zeitz}

@@

@@

For sake of keeping this section self-contained, we now briefly reiterate the details of our configuration.
The stretch limited to $\epsilon = 0.25$, i.e. for any path $P = (u,\dots,v)$ in the alternative graph $w(P) \leq (1+\epsilon) \cdot \dist(u,v)$.
Shortest path edges are penalized multiplicative with a factor of $\psi = 1.1$, i.e. when an edges was $k$ times on a shortest path its weight will be $w_q = w_{\ell}\cdot\psi^k$.
We also penalize edges incident to shortest paths with an asymmetric additive rejoin penalty.
An edge $uv$ where $u$ is on a shortest path but $v$ is not will get its weight increased by $\psi_r \cdot \dist_{w_{\ell}}(s,t) \cdot \frac{\dist_{w_q}(s,u)}{\dist_{w_q}(s,t)}$.
An edge $uv$ where $v$ is on a shortest path but $u$ is not will get its weight increased by $\psi_r \cdot \dist_{w_{\ell}}(s,t) \cdot \frac{\dist_{w_q}(v,t)}{\dist_{w_q}(s,t)}$.
$\psi_r$ is set to 0.01.
To avoid over-penalization, we count the times a \emph{node} was on a shortest path and do not apply penalties, when this number exceeds $k_{\max} := \lceil\log_{\psi}(1+\epsilon)\rceil + 2$.
Shortest paths are split into segments not yet contained in the alternative graph.
A segment is only added if it is long enough (at least $0.05 \cdot \dist_{w_{\ell}}(s,t)$) and does not violate the maximum stretch condition.
We terminate the algorithm when any of the following conditions becomes true:
\begin{itemize}
	\item All nodes on the current shortest path have been penalized $k_{\max}$ times.
	\item 10 ore more segments have been added to the alternative graph.
	\item The shortest path is longer than $(1+\epsilon) \cdot \dist_{w_{\ell}}(s,t)$ with respect to the original metric.
	\item The shortest path is longer than $(1+\epsilon) \cdot \psi + 2\psi_r \cdot \dist_{w_{\ell}}(s,t)$ with respect to the penalized metric.
\end{itemize}
The last two stopping criteria can both be utilized for additional pruning in the A*.
As a final optimization, we run the forward and backward search in parallel in two threads.
